Computing Entropies With Nested Sampling

### 2017-06-19 paper/ms.tex
Minor edits

\section{Example 1: Measuring the mean of a gaussian}

This example demonstrates how the algorithm may be used to determine the
entropy for a quantity whose distribution can only be sampled.
Consider the basic statistics problem of inferring a quantity $\mu$ from
100 observations $\d = \{d_1, ..., d_{100}\}$ whose
probability distribution (conditional on $\mu$) is
\begin{align}
p(d_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \d &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} d_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}
The true value of the differential entropy $H(\d)$ is available analytically
in this case, and its value is $146.499$. However, in most situations, the
entropy of a marginal distribution is not available in closed form.

>>>>

\section{Example 1: Entropy of a prior for the data}

This example demonstrates how the algorithm may be used to determine the
entropy for a quantity whose distribution can only be sampled.
Consider the basic statistics problem of inferring a quantity $\mu$ from
100 observations $\d = \{d_1, ..., d_{100}\}$ whose
probability distribution (conditional on $\mu$) is
\begin{align}
p(d_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \d &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} d_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}
The true value of the differential entropy $H(\d)$ is available analytically
in this case, and its value is $146.499$ nats. However, in most situations, the
entropy of a marginal distribution is not available in closed form.
